\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-10-09 draft.tex
fix missing \tad and order of \tad and \bta throughout text

I represent the total probability that the antidumping duties will be renewed as $R(\bta)=r(e(\bta,\tad),\bta,\tad)$ where $e(\bta,\tad)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition. We next examine the question of how the total renewal probability varies as both a direct and indirect function of both trade agreement tariffs and antidumping duties, as well as industry profitability and political influence. Each result must take into account that the variable of interest can have both a direct effect on the renewal probability and an indirect effect through lobbying incentives.

@@

\begin{result}
	The total probability that the antidumping duties will be renewed is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta)}{\partial  \tau^a} \leq 0$).
	\label{res:bcomB}
\end{result}

\noindent When $\tau^a$ is higher, the government agency becomes less likely to renew the antidumping duties, for three reasons. First, the government prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta)$ indirectly (Lemma~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the government's preferred tariff further (Lemma~\ref{res:bincC}).

@@

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive. Labeling the numerator of that expression $Z(\tad,\bta)$, the derivative of this quantity with respect to $\tau^{a}$ is 
\begin{equation}
  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\tad,\bta) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:a}
\end{equation}

@@

Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $Z(\tad,\bta)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign). With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.

@@

We can rewrite $\frac{\partial r(e,\bta)}{\partial  \tau^a} = -\frac{\partial F_\ga (Z(\tad,\bta))}{\partial \tau^a} = -\frac{\partial F_\ga (Z(\tad,\bta))}{\partial Z(\tad,\bta)} \frac{\partial Z(\tad,\bta)}{\partial \tau^a} = - f_\ga \frac{\partial Z(\tad,\bta)}{\partial \tau^a}$, where $F_\ga (Z(\tad,\bta))$ is the CDF of $\ga$ and $f_\ga (Z(\tad,\bta))$ is the pdf of $\ga$ and $Z(\tad,\bta)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.

Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\tad,\bta))}{\partial \tau^a} \right) = 
	   - f_\ga \frac{\partial^2 Z(\tad,\bta)}{\partial \tau^a \partial e} - [\frac{\partial Z(\tad,\bta)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\tad,\bta)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\tad,\bta)$ does not depend on $e$. The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\tad,\bta)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$. Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.  $\hfill\blacksquare$

\vskip.4in
\noindent \textbf{\hypertarget{Pr_bincC}{Proof of Lemma~\ref{res:bincC}}}:\\
\noindent The left side of the inequality in Expression~\ref{eq:b_ex}, $Z(\tad,\bta)$, does not depend on $e$. Thus we have $r(e,\bta,\tad) = \Pr [Z < \ga(e,\ve) ] = 1 - F_{\ga}(\ga=Z)$ where $F_{\ga}(\ga=Z) = F_{\ta}(\ta=h^{-1}(\ga,e))$ by the Change of Variables Theorem and Assumption~\ref{as:ga_ta} with $\ga = h(e,\ta)$ giving the change of variable.

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_bcomB}{Proof of Result~\ref{res:bcomB}}}: \\
$	\frac{\partial R(\bta)}{\partial \tau^a} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a}$. $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}. $\frac{\partial e}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:lobby}. $\frac{\partial r}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:leg_a}. Thus the entire expression is non-positive. $\hfill\blacksquare$

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_astar}{Proof of Result~\ref{res:leg_astar}}}: \\
$	\frac{\partial R(\bta)}{\partial \tau^{*a}} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^{*a}} + \frac{\partial r}{\partial \tau^{*a}}$. $\frac{\partial r}{\partial \tau^{*a}}$ is zero because Expression~\ref{eq:b_ex}, after simplification, is not a function of $\tau^{*a}$. $\frac{\partial e}{\partial \tau^{*a}}$ is also zero because Equation~\ref{eq:lobbyfoc} is not a function of $\tau^{*a}$. Thus the entire expression is zero. $\hfill\blacksquare$

>>>>

I represent the total probability that the antidumping duties will be renewed as $R(\bta,\tad)=r(e(\bta,\tad),\bta,\tad)$ where $e(\bta,\tad)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition. We next examine the question of how the total renewal probability varies as both a direct and indirect function of both trade agreement tariffs and antidumping duties, as well as industry profitability and political influence. Each result must take into account that the variable of interest can have both a direct effect on the renewal probability and an indirect effect through lobbying incentives.

@@

\begin{result}
	The total probability that the antidumping duties will be renewed is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \tau^a} \leq 0$).
	\label{res:bcomB}
\end{result}

\noindent When $\tau^a$ is higher, the government agency becomes less likely to renew the antidumping duties, for three reasons. First, the government prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta,\tad)$ indirectly (Lemma~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the government's preferred tariff further (Lemma~\ref{res:bincC}).

@@

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive. Labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is 
\begin{equation}
  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:a}
\end{equation}

@@

Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $Z(\bta,\tad)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign). With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.

@@

We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial  \tau^a} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \tau^a} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \tau^a}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.

Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tau^a \partial e} - [\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$. Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.  $\hfill\blacksquare$

\vskip.4in
\noindent \textbf{\hypertarget{Pr_bincC}{Proof of Lemma~\ref{res:bincC}}}:\\
\noindent The left side of the inequality in Expression~\ref{eq:b_ex}, $Z(\bta,\tad)$, does not depend on $e$. Thus we have $r(e,\bta,\tad) = \Pr [Z < \ga(e,\ve) ] = 1 - F_{\ga}(\ga=Z)$ where $F_{\ga}(\ga=Z) = F_{\ta}(\ta=h^{-1}(\ga,e))$ by the Change of Variables Theorem and Assumption~\ref{as:ga_ta} with $\ga = h(e,\ta)$ giving the change of variable.

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_bcomB}{Proof of Result~\ref{res:bcomB}}}: \\
$	\frac{\partial R(\bta,\tad)}{\partial \tau^a} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a}$. $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}. $\frac{\partial e}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:lobby}. $\frac{\partial r}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:leg_a}. Thus the entire expression is non-positive. $\hfill\blacksquare$

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_astar}{Proof of Result~\ref{res:leg_astar}}}: \\
$	\frac{\partial R(\bta,\tad)}{\partial \tau^{*a}} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^{*a}} + \frac{\partial r}{\partial \tau^{*a}}$. $\frac{\partial r}{\partial \tau^{*a}}$ is zero because Expression~\ref{eq:b_ex}, after simplification, is not a function of $\tau^{*a}$. $\frac{\partial e}{\partial \tau^{*a}}$ is also zero because Equation~\ref{eq:lobbyfoc} is not a function of $\tau^{*a}$. Thus the entire expression is zero. $\hfill\blacksquare$
